Exploratory Plots

### 2020-09-04 exploratory/2020/sub3_fit_subsets.Rmd
Update plots

## Runtime
```{r}
benchmarks_fit <-
  read_tsv(here('subworkflows/2_fit_reference_db/results/benchmarks.tsv'))
benchmarks_fit %>% 
    group_by(dataset, method) %>%
    ggplot(aes(x = method, y = s, color = dataset)) +
    geom_boxplot() +
    scale_color_manual(values = dataset_colors) +
    #facet_wrap("ref_weight") +
    ylim(0,2100) +
    labs(y = 'seconds') +
    theme(axis.title.x = element_blank())
```

## Fraction of sequences that map to the reference
```{r fraction_reads_mapped}
fractions <- read_tsv(here('subworkflows/3_fit_sample_subset/results/fraction_reads_mapped.tsv'))
fractions %>% 
  ggplot(aes(x=dataset, y=fraction_mapped, color=dataset)) +
  geom_boxplot(alpha = 0.5) +
  scale_color_manual(values = dataset_colors) +
  facet_wrap("ref_weight") +
  ylim(0, 1) +
  labs(title="Sequences mapped during closed-reference OptiFit")
```

>>>>

## Runtime
```{r}
benchmarks_fit <-
  read_tsv(here('subworkflows/2_fit_reference_db/results/benchmarks.tsv'))
# TODO: show number of unique seqs 
benchmarks_fit %>% 
    group_by(dataset, method) %>%
    ggplot(aes(x = method, y = s, color = dataset)) +
    geom_boxplot() +
    scale_color_manual(values = dataset_colors) +
    #facet_grid(ref_weight ~ .) +
    ylim(0,2100) +
    labs(y = 'seconds') +
    theme(axis.title.x = element_blank())
```

## Fraction of sequences that map to the reference
```{r fraction_reads_mapped}
fractions <- read_tsv(here('subworkflows/3_fit_sample_subset/results/fraction_reads_mapped.tsv'))
fractions %>% 
  ggplot(aes(x=ref_frac, y=fraction_mapped, color=dataset)) +
  geom_point(alpha = 0.5) +
  scale_color_manual(values = dataset_colors) +
  facet_grid(ref_weight ~ dataset) +
  ylim(0, 1) +
  labs(title="Sequences mapped during closed-reference OptiFit")
```
